Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/approach.tex
approach iter 2

The ultimate goal of this project is to infer invariants in a
distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
state variables. We define distributed state variables, as variables
that are stored in one node whose values are affected or determined by
the other remote node in the distributed system. It should be noted that
these variables are only a part of the state in a distributed system
at a given time. For our case we assume that these capture a
significant portion of the state. Consider the code samples
Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
communication between two nodes in a distributed system. The
communication between the nodes can be depicted as shown in
Figure~\ref{fig:sample_code_diag}. We need to infer the equality
between elements in each pair \texttt{(a,first),
(b,second),(sum,result)} and also the properites: \texttt{(result = a
+ b)} and \texttt{(sum = first + second)}.

@@

The naive approach for inferring these invariants will be to dump all
state varaible values at all program points and feed them to an
invariant detector like daikon\cite{ernst2007daikon}. But given the
number of program points and huge number of variables in a relatively
large program this approach is not scalable. So we propose 2 main
optimizations to reduce the number of program point, variable value
combinations.

@@

>>>>

The ultimate goal of this project is to infer invariants in a
distributed system. For the scope of this project we will consider a
system with 2 nodes. Before inferring invariants we need to identify
likely distributed state variables. We define distributed state
variables, as variables that are stored in one node whose values are
affected or determined by the other remote node in the distributed
system. It should be noted that these variables are only a part of the
state in a distributed system at a given time. For our case we assume
that these capture a significant portion of the state. Consider the
code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1}
showing the communication between two nodes in a distributed system.
This conversation is depicted visually in
Figure~\ref{fig:sample_code_diag}. Here it will be useful to to infer
the equality between elements in each pair \texttt{(a,first),
(b,second),(sum,result)} and also the properites: \texttt{(result = a
+ b)} and \texttt{(sum = first + second)}.

@@

The naive approach for inferring these invariants will be to dump all
state varaible values at all program points and feed them to an
invariant detector like daikon\cite{ernst2007daikon}. But given the
number of program points and huge number of variables in a relatively
large program this approach is not scalable. So we propose two main
optimizations to reduce the number of program point, variable value
combinations.

@@

Since there can be multiple points annotated in a program by a
developer, vector clocks will be used to partially order annotation
pairs in the two programs. This will also help to invalidate
annotations put at irrelevant locations by the developer.
